The state of knowledge for marine invertebrate biodiversity in the continental US

### 2017-09-27 manuscript.Rmd
fix typo in figure legend
[fix #63] first draft of acknowledgments
This reverts commit a0dc16a085d00251ad7faa81a049fce791c1d1cd.

```{r id_though_time, fig.cap='Proportion of marine invertebrate specimens collected through time identified at the species level. Trend lines are  B-splines of the 3rd degree polynomial. For all groups, we observe a decline in the proportion of specimens collected identified at the species leveld. (\\#fig:identification-through-time)'}
knitr::include_graphics("figures/idigbio_identification_level_through_time.pdf")
```

@@

>>>>

```{r id_though_time, fig.cap='Proportion of marine invertebrate specimens collected through time identified at the species level. Trend lines are  B-splines of the 3rd degree polynomial. For all groups, we observe a decline in the proportion of specimens collected identified at the species level. (\\#fig:identification-through-time)'}
knitr::include_graphics("figures/idigbio_identification_level_through_time.pdf")
```

@@

## Acknowledgments

We thank WoRMS, BOLD, iDigBio, OBIS, MarineRegions, NCBI, and all other data providers that aim to make more accessible biodiversity data. We would also like to acknowledge the efforts of rOpenSci (https://ropensci.org) for developping tools to make these data sources available in R. We are grateful to Julie Allen, Robert Lasley, Kevin Love, and Pamela Soltis, for providing suggestions that improved the manuscript.
